Fun With Melanogaster 
========================================================

```{r include=FALSE}
library(knitr)
library(markdown)
require(ggplot2)
require (proto)
require(gtable)
require(gridExtra)
require(grid)
require(digest)
require(plotrix)
require(devtools)
```

```{r}
behave<-read.table("~/Desktop/melfun.csv", header=TRUE, sep=",")
```

```{r}
behave1<-subset(behave, replicate=="a")
behave2<-na.omit(behave1)
```

```{r include=FALSE}
require(ggplot2)
require(GGally)
require(CCA)
```

```{r}
ecospermomics<-behave2[,6:8]
ggpairs(ecospermomics)
```


```{r}
cor.test(behave2$male,behave2$SpermTransferred,method="spearman")
cor.test(behave2$male,behave2$SpermTransferred,method="pearson")
```
========================================================
## Reshape2 & dplyr ()


install.packages('dplyr')
install.packages('reshape2') 
library(reshape2)
library(dplyr)
install.packages('plyr')
library(plyr)

```{r include=FALSE}
library(plyr)
```


devtools::install_github("hadley/dplyr") LATEST PACKAGE UNDER DEVELOPMENT IF NEEDED

melted <- melt(data, id.vars=c("behave2$genotype", "behave2$SpermTransferred"))
library(dplyr)
grouped <- group_by(melted, behave2$genotype, behave2$SpermTransferred)

=============
##  Summary Stats using ddply in the plyr package

```{r}
ddply(behave2, .(genotype), numcolwise(mean))
```

```{r}
ddply(behave2, "genotype", summarise, var(offspring))
```
=======
This below function allows me to call all correlations by group of genotype.  I want to test this on the shapiro.test to see if it will apply.

```{r}
 ddply(behave2, .(genotype), summarize,
       r=cor.test(SpermTransferred, male)$estimate,
       p=cor.test(SpermTransferred, male)$p.value)
```

```{r}
ddply(behave2, "genotype", summarise, var(Area))
```

```{r}
ddply(behave2, "genotype", summarise, var(HW))
```

```{r}
ddply(behave2, "genotype", summarise, var(SpermTransferred))
```

=======
Summary stats using a sqrt transformation.

behave<-read.table("~/Desktop/melfununo.csv", header=TRUE, sep=",")



